Summary Tables

### 2021-07-19 summary_tables.Rmd
Update distance categories
Regen

@@

## Case study specific propensities

|accra|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 95.5|27.9|2.6 |
| cycle | 0.6|0.7|0.4 |
| car | 0.9|12.4|17.2 |
| motorcycle | 0.0|0.0|1.3 |
| bus | 2.4|48.3|71.8 |

|bangalore|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 75.0|23.0|1.0 |
| cycle | 2.3|9.8|1.1 |
| car | 1.0|4.4|6.4 |
| motorcycle | 5.1|33.9|63.2 |
| bus | 15.1|24.3|25.0 |

|belo_horizonte|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 89.2|8.7|0.3 |
| cycle | 1.6|2.7|0.2 |
| car | 7.3|65.6|47.1 |
| motorcycle | 1.3|10.1|5.3 |
| bus | 0.4|11.1|43.1 |

|bogota|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 91.0|20.9|1.2 |
| cycle | 4.9|12.1|2.0 |
| car | 1.5|26.7|29.3 |
| motorcycle | 0.5|5.9|6.5 |
| bus | 0.8|20.7|56.8 |

|buenos_aires|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 80.2|2.9|0.1 |
| cycle | 7.4|3.6|0.3 |
| car | 6.2|34.5|21.4 |
| motorcycle | 0.6|2.8|1.2 |
| bus | 3.5|50.1|51.0 |

|cape_town|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 84.1|5.3|1.9 |
| cycle | 0.2|0.5|0.1 |
| car | 8.0|55.6|48.3 |
| motorcycle | 0.0|0.7|0.4 |
| bus | 6.9|34.8|33.3 |

|delhi|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 84.4|10.1|0.9 |
| cycle | 2.0|7.6|3.7 |
| car | 2.4|17.3|21.4 |
| motorcycle | 5.6|30.1|26.5 |
| bus | 0.7|24.7|32.7 |

|mexico_city|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 89.9|3.5|0.0 |
| cycle | 2.5|3.2|0.2 |
| car | 2.2|37.9|31.8 |
| motorcycle | 0.4|3.2|0.9 |
| bus | 1.7|34.8|33.8 |

|santiago|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 84.0|3.9|0.0 |
| cycle | 6.2|6.1|0.5 |
| car | 8.1|58.7|32.3 |
| motorcycle | 0.1|2.2|1.1 |
| bus | 0.5|20.5|28.8 |

|sao_paulo|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 82.7|1.9|0.0 |
| cycle | 1.3|1.4|0.1 |
| car | 12.6|65.4|37.0 |
| motorcycle | 0.8|3.2|1.9 |
| bus | 1.0|21.3|28.9 |

|vizag|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 86.2|19.7|0.1 |
| cycle | 2.6|6.6|2.1 |
| car | 0.6|2.4|2.8 |
| motorcycle | 6.9|24.3|24.6 |
| bus | 0.8|26.9|55.5 |

>>>>

0-2 km = \{trip distance < 2\}

2-6 km = \{2 <= trip distance < 6\}

@@

## Case study specific propensities
get_scen_settings <- ithimr::get_scenario_settings()
